An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-22 indicators/paper/pnas-suppl-template.tex
Fill out supplement template

\title{Your main manuscript title}
\author{Author1, Author2 and Author3 (complete author list)}
\correspondingauthor{Corresponding Author name.\\E-mail: author.two@email.com}

>>>>

\title{An Open Repository of Real-Time COVID-19 Indicators}
\author{Alex Reinhart, Logan Brooks, Maria Jahja, Aaron Rumack, Jingjing Tang,
  et al.}
\correspondingauthor{Alex Reinhart.\\E-mail: areinhar@stat.cmu.edu}
